Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-27 supplementals/manuscript_supplementals.tex
supplemental materials

---
title: |
  | Supplemental Materials for
  | Quantifying Stability and Change in Personal Culture Using Panel Data
author: 
- 
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    toc: true
geometry: margin=1in 
mainfont: Times New Roman
fontsize: 12pt
header-includes:
  \usepackage{fontspec}
  \usepackage{longtable}
  \usepackage{multirow}
  \usepackage{array}
  \usepackage{booktabs}
  \usepackage{dcolumn}
  \usepackage{lscape}
  \usepackage{caption}
  \newcommand{\blandscape}{\begin{landscape}}
  \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.align = "center")
```

\newpage
\blandscape

# Supplemental Materials A

In Table A1, we present the survey items, corresponding labels and topic indicators, as well as the variances calculated from our estimations: V(C) refers to intraindividual change, V(D) refers to interindividual differences, and V(R) refers to residual variance. We also present the $\omega$ values.

```{=latex}

@@

```

\elandscape
\newpage

# Supplemental Materials B

Table B1 presents the full set of coefficients from an OLS model regressing $\omega$ on multiple covariates, described in Figure 2 in the main manuscript.

```{=latex}
\begin{table}[ht]
\begin{center}
\caption*{Table B1: Regression Model} 
\label{tab:sometab}
\begin{tabular}{l c c}
\hline
 & Estimates & SE \\
\hline
N Part. (log)                                       & $0.01$        
                                                    & $(0.01)$      \\
Duration                                            & $-0.00$ 
                                                    & $(0.00)^{***}$ \\
N Waves (Part.)                                     & $0.00$        
                                                    & $(0.00)$      \\
N Waves (Survey)                                    & $-0.00$       
                                                    & $(0.00)$      \\
Wave 1 (Decade)                                     & $-0.01$  
                                                    & $(0.00)^{**}$  \\
Panels: BHPS                                        & $0.08$        
                                                    & $(0.05)$      \\
Panels: GSS                                         & $0.04$        
                                                    & $(0.05)$      \\
Panels: HILDA                                       & $0.08$        
                                                    & $(0.05)$      \\
Panels: PSID                                        & $0.09$    
                                                    & $(0.04)^{*}$  \\
Panels: SHP                                         & $0.06$        
                                                    & $(0.05)$      \\
Panels: SOEP                                        & $0.06$        
                                                    & $(0.05)$      \\
Panels: UKHLS                                       & $0.09$        
                                                    & $(0.06)$      \\
Topics: Environment and Climate                     & $0.04$   
                                                    & $(0.01)^{**}$      \\
Topics: Gender and Family                           & $0.00$        
                                                    & $(0.01)$      \\
Topics: Health and Morale                           & $0.03$   
                                                    & $(0.01)^{**}$      \\
Topics: National Identity, Ethnicity, Immigration   & $0.02$        
                                                    & $(0.01)$      \\
Topics: Occupation and Education                    & $-0.02$       
                                                    & $(0.02)$      \\
Topics: Religion and Spirituality                   & $-0.00$       
                                                    & $(0.01)$      \\
Topics: Social Life, Social Cohesion and Trust      & $0.03$  
                                                    & $(0.01)^{***}$      \\
Topics: Subjective SES                              & $0.03$    
                                                    & $(0.01)^{*}$      \\
\hline
Adjusted R$^2$                                      & $0.77$     &   \\
N                                                   & $609$      &  \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
\end{center}
\end{table}
```

@@

# Supplemental Materials C

Figure C1 presents the alternative strategy we used to understand the effects of duration on intraindividual change. First, we restricted the sample such that we have at least 4 waves of observations for all participants. This reduced the number of items to 249. We then fitted the Life Course Adaption models to this sample. Second, we removed the last wave from all the observations, and refit the same models once more. In the final step, we calculated the $\omega$ values for each item. The Figure C1 shows a scatterplot for these two sets of observations.

```{=latex}
\begin{figure}[ht]
\begin{center}
\caption*{Figure C1: Difference in $\omega$ Across Two Sample Specifications} 
```
```{r fig3, out.width = "5in"}
knitr::include_graphics("../figures/figure_S3.png")
```
```{=latex}
\end{center}
\end{figure}
```

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{fontspec} \usepackage{longtable} \usepackage{multirow} \usepackage{array} \usepackage{booktabs} \usepackage{dcolumn} \usepackage{lscape} \usepackage{caption} \newcommand{\blandscape}{\begin{landscape}} \newcommand{\elandscape}{\end{landscape}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplemental Materials for\\
Quantifying Stability and Change in Personal Culture Using Panel Data}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage
\begin{landscape}

\hypertarget{supplemental-materials-a}{%
\section{Supplemental Materials A}\label{supplemental-materials-a}}

In Table A1, we present the survey items, corresponding labels and topic
indicators, as well as the variances calculated from our estimations:
V(C) refers to intraindividual change, V(D) refers to interindividual
differences, and V(R) refers to residual variance. We also present the
\(\omega\) values.

@@

\end{landscape}
\newpage

\hypertarget{supplemental-materials-b}{%
\section{Supplemental Materials B}\label{supplemental-materials-b}}

Table B1 presents the full set of coefficients from an OLS model
regressing \(\omega\) on multiple covariates, described in Figure 2 in
the main manuscript.

\begin{table}[ht]
\begin{center}
\caption*{Table B1: Regression Model} 
\label{tab:sometab}
\begin{tabular}{l c c}
\hline
 & Estimates & SE \\
\hline
N Part. (log)                                       & $0.01$        
                                                    & $(0.01)$      \\
Duration                                            & $-0.00$ 
                                                    & $(0.00)^{***}$ \\
N Waves (Part.)                                     & $0.00$        
                                                    & $(0.00)$      \\
N Waves (Survey)                                    & $-0.00$       
                                                    & $(0.00)$      \\
Wave 1 (Decade)                                     & $-0.01$  
                                                    & $(0.00)^{**}$  \\
Panels: BHPS                                        & $0.08$        
                                                    & $(0.05)$      \\
Panels: GSS                                         & $0.04$        
                                                    & $(0.05)$      \\
Panels: HILDA                                       & $0.08$        
                                                    & $(0.05)$      \\
Panels: PSID                                        & $0.09$    
                                                    & $(0.04)^{*}$  \\
Panels: SHP                                         & $0.06$        
                                                    & $(0.05)$      \\
Panels: SOEP                                        & $0.06$        
                                                    & $(0.05)$      \\
Panels: UKHLS                                       & $0.09$        
                                                    & $(0.06)$      \\
Topics: Environment and Climate                     & $0.04$   
                                                    & $(0.01)^{**}$      \\
Topics: Gender and Family                           & $0.00$        
                                                    & $(0.01)$      \\
Topics: Health and Morale                           & $0.03$   
                                                    & $(0.01)^{**}$      \\
Topics: National Identity, Ethnicity, Immigration   & $0.02$        
                                                    & $(0.01)$      \\
Topics: Occupation and Education                    & $-0.02$       
                                                    & $(0.02)$      \\
Topics: Religion and Spirituality                   & $-0.00$       
                                                    & $(0.01)$      \\
Topics: Social Life, Social Cohesion and Trust      & $0.03$  
                                                    & $(0.01)^{***}$      \\
Topics: Subjective SES                              & $0.03$    
                                                    & $(0.01)^{*}$      \\
\hline
Adjusted R$^2$                                      & $0.77$     &   \\
N                                                   & $609$      &  \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
\end{center}
\end{table}

@@

\hypertarget{supplemental-materials-c}{%
\section{Supplemental Materials C}\label{supplemental-materials-c}}

Figure C1 presents the alternative strategy we used to understand the
effects of duration on intraindividual change. First, we restricted the
sample such that we have at least 4 waves of observations for all
participants. This reduced the number of items to 249. We then fitted
the Life Course Adaption models to this sample. Second, we removed the
last wave from all the observations, and refit the same models once
more. In the final step, we calculated the \(\omega\) values for each
item. The Figure C1 shows a scatterplot for these two sets of
observations.

\begin{figure}[ht]
\begin{center}
\caption*{Figure C1: Difference in $\omega$ Across Two Sample Specifications}

\begin{center}\includegraphics[width=5in]{../figures/figure_S3} \end{center}

\end{center}
\end{figure}

\end{document}

### 2023-09-27 tables/table_A1.tex
supplemental materials

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{fontspec} \usepackage{longtable} \usepackage{multirow} \usepackage{array} \usepackage{booktabs} \usepackage{dcolumn} \usepackage{lscape} \usepackage{caption} \newcommand{\blandscape}{\begin{landscape}} \newcommand{\elandscape}{\end{landscape}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplemental Materials for\\
Quantifying Stability and Change in Personal Culture Using Panel Data}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage
\begin{landscape}

\hypertarget{supplemental-materials-a}{%
\section{Supplemental Materials A}\label{supplemental-materials-a}}

In Table A1, we present the survey items, corresponding labels and topic
indicators, as well as the variances calculated from our estimations:
V(C) refers to intraindividual change, V(D) refers to interindividual
differences, and V(R) refers to residual variance. We also present the
\(\omega\) values.

\begin{scriptsize}
\begin{longtable}{|p{1.75in}|p{0.3in}|p{0.3in}|p{0.3in}|p{0.3in}|p{2.5in}|p{2.5in}}
\caption*{Table A1: The Descriptives of Variables Used}
\\

@@

\multicolumn{1}{l}{} & \emph{\textbf{ω}} & \textbf{V(C)} & \textbf{V(D)} & \textbf{V(R)} & \textbf{Label} & \textbf{Topic} \\ 

@@

\end{scriptsize}

\end{landscape}
\newpage

\hypertarget{supplemental-materials-b}{%
\section{Supplemental Materials B}\label{supplemental-materials-b}}

Table B1 presents the full set of coefficients from an OLS model
regressing \(\omega\) on multiple covariates, described in Figure 2 in
the main manuscript.

\begin{table}[ht]
\begin{center}
\caption*{Table B1: Regression Model} 
\label{tab:sometab}
\begin{tabular}{l c c}
\hline
 & Estimates & SE \\
\hline
N Part. (log)                                       & $0.01$        
                                                    & $(0.01)$      \\
Duration                                            & $-0.00$ 
                                                    & $(0.00)^{***}$ \\
N Waves (Part.)                                     & $0.00$        
                                                    & $(0.00)$      \\
N Waves (Survey)                                    & $-0.00$       
                                                    & $(0.00)$      \\
Wave 1 (Decade)                                     & $-0.01$  
                                                    & $(0.00)^{**}$  \\
Panels: BHPS                                        & $0.08$        
                                                    & $(0.05)$      \\
Panels: GSS                                         & $0.04$        
                                                    & $(0.05)$      \\
Panels: HILDA                                       & $0.08$        
                                                    & $(0.05)$      \\
Panels: PSID                                        & $0.09$    
                                                    & $(0.04)^{*}$  \\
Panels: SHP                                         & $0.06$        
                                                    & $(0.05)$      \\
Panels: SOEP                                        & $0.06$        
                                                    & $(0.05)$      \\
Panels: UKHLS                                       & $0.09$        
                                                    & $(0.06)$      \\
Topics: Environment and Climate                     & $0.04$   
                                                    & $(0.01)^{**}$      \\
Topics: Gender and Family                           & $0.00$        
                                                    & $(0.01)$      \\
Topics: Health and Morale                           & $0.03$   
                                                    & $(0.01)^{**}$      \\
Topics: National Identity, Ethnicity, Immigration   & $0.02$        
                                                    & $(0.01)$      \\
Topics: Occupation and Education                    & $-0.02$       
                                                    & $(0.02)$      \\
Topics: Religion and Spirituality                   & $-0.00$       
                                                    & $(0.01)$      \\
Topics: Social Life, Social Cohesion and Trust      & $0.03$  
                                                    & $(0.01)^{***}$      \\
Topics: Subjective SES                              & $0.03$    
                                                    & $(0.01)^{*}$      \\
\hline
Adjusted R$^2$                                      & $0.77$     &   \\
N                                                   & $609$      &  \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
\end{center}
\end{table}

\newpage

\hypertarget{supplemental-materials-c}{%
\section{Supplemental Materials C}\label{supplemental-materials-c}}

Figure C1 presents the alternative strategy we used to understand the
effects of duration on intraindividual change. First, we restricted the
sample such that we have at least 4 waves of observations for all
participants. This reduced the number of items to 249. We then fitted
the Life Course Adaption models to this sample. Second, we removed the
last wave from all the observations, and refit the same models once
more. In the final step, we calculated the \(\omega\) values for each
item. The Figure C1 shows a scatterplot for these two sets of
observations.

\begin{figure}[ht]
\begin{center}
\caption*{Figure C1: Difference in $\omega$ Across Two Sample Specifications}

\begin{center}\includegraphics[width=5in]{../figures/figure_S3} \end{center}

\end{center}
\end{figure}

\end{document}

>>>>

\begin{longtable}{l|rrrrll}
\caption*{
{\large \textbf{Descriptives of variables}}
} \\ 

@@

\multicolumn{1}{l}{} & \emph{\textbf{ω}} & \textbf{Within variance} & \textbf{Between variance} & \textbf{Residual variance} & \textbf{Label} & \textbf{Topic} \\ 

@@
